Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-27 Tex/Old text/chapters/appendixB.tex
Thesis update

Here we describe the two tools created during the PhD process to implement and validate the two scientific methodologies of the thesis.

@@

During the PhD process, the techniques from computer science and proposed to tackle issues related to solar photovoltaic systems became algorithms and codes. Those codes became tools, and the tools were used during comparative with simulation tool in order to validate the technique.

In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation.

@@

\subsubsection{Automated Verification Tool (PV System validation)}

@@

\subsubsection{Automated Synthesis Tool (PV System Optimal Sizing)}

@@

\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions)

@@

\section{How to use it}
The only block that demands user intervention from user in order to input data is the block 1 of both tools.

@@

\section{Automated Verification with Incremental ESBMC}
Here 123

\section{Automated Synthesis with CPAchecker}
Here 4321

>>>>

Here we describe the two tools created with the target to implement and validate the two scientific methodologies of the thesis.

@@

During the PhD process, the techniques from computer science and proposed to tackle issues related to solar photovoltaic systems became algorithms and codes. Those codes became tools, and the tools were used during comparative with simulation tool in order to validate the techniques.

In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since that we aimed to evaluate different .

@@

\subsection{Automated Verification Tool (PV System validation)}
\label{sec:automatedverification}

@@

\subsection{Automated Synthesis Tool (PV System Optimal Sizing)}
\label{sec:automatedsynthesis}

@@

\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking)

@@

\section{How to use it}

The only block that demands user intervention from user in order to input data is the block 1 of both tools. If it is aimed to change the mathematical model adopted, so coding must be done in block 3 of automated verification tool and in block 2 of automated synthesis tool.

@@

\subsection{Automated Verification with Incremental ESBMC}

Here we describe specifically how to use the code explained in previous section (\ref{sec:automatedverification}) using the incremental ESBMC with Z3 solver, that presented the better performance during the comparative with other verifiers. However, in \ref{sec:setup} it was showed how to use the code with other verifiers.

ESBMC can be downloaded from its GitHub in \url{https://github.com/esbmc/esbmc}. Installation commands can be found in \url{https://ssvlab.github.io/esbmc/documentation.html}.

Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3.

Where:
\begin{itemize}
\item -no-bounds-check: says to the verifier to not perform array bound check (the aim is not to check array bound violation);
\item -\phantom{}-no-pointer-check: says to the verifier to not check if there is pointer violation;
\item -\phantom{}-unwind 100: it limits the bound of search (100 in this case);
\item -\phantom{}-smt-during-symex: enable incremental SMT solving;
\item -\phantom{}-smt-symex-guard: call the solver during symbolic execution;
\item -\phantom{}-z3: uses Z3 as solver.
\end{itemize}

Some results issued by the ESBMC verifier were depicted in \ref{sec:ESBMCverification} when performing the case studies.

\subsection{Automated Synthesis with CPAchecker}

Here we describe specifically how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, that presented the better performance during the comparative with other verifiers. However, in \ref{sec:synthesissetup} it was showed how to use the code with other verifiers.

The CPAchecker can be downloaded from its web site in \url{https://cpachecker.sosy-lab.org/}. There are versions available to Linux and MS-Windows operational systems.

Install a Java Runtime Environment which is at least Java 8 compatible (e.g., Oracle JRE, OpenJDK). Cf. the web site \url{http://java.oracle.com/}.

The command-line in Linux is: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c.

Worth to mention that the default heap size is 1200m (or 1.2 GB of RAM), however it is indicated to specify a large value with '-heap' if you have more RAM memory available. In our case, we adjusted the heap to 64000m (64 GB).

Other important issue is the time-out of the execution process: the parameter 'limits.time.cpu' at the file 'resource-limits.properties' in folder 'config/includes' must be edited according the desired value. In our case, 'limits.time.cpu = 14400s', i.e., 14400 seconds or 240 minutes or 4 hours.

Some results, reports and graphics, issued by the CPAchecker verifier were depicted in \ref{sec:synthesisresults}.
